---
title: "download_osf_data"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim of this project is to test how to download data from the open science
framework (OSF) using R and embed that process into code that is kept on GitHub.

So, let's see if we can load data directly from the OSF using the R package 
{osfr}.

## load the libraries that we will be using ## 

## install packages ##

```{r}
# install.packages(c("tidyverse", "osfr", "here"))
```

take a snapshot of loaded packages and update the lock.file using renv

```{r snapshot-renv}
# take a snapshot and update the lock.file
# renv::snapshot() # this is only necessary when new packages or installed or packages are updated.
```

## load packages ##

```{r load-pkg}
pkg <- c("tidyverse", "osfr", "here")

lapply(pkg, library, character.only = TRUE)
```

## download the data from the OSF using osfr ##

```{r}
# retrieve OSF data
osf_data <-
    # retrieve the OSF (main) project
    osf_retrieve_node("jc82t") %>% ## this is just one project picked at random
    # list files in this repository - there must be a more efficient way than this...
    osf_ls_files(pattern = "data") %>%
    osf_ls_files(pattern = "prior") %>%
    osf_ls_files(pattern = "d1") %>% 
    osf_download(path = "./data/", conflicts = "overwrite") ## set the path to download the data into, use overwrite if necessary
head(osf_data)
glimpse(osf_data)
```

Now the file named d1.csv is downloaded to the folder name /data/ in the 
directory. It feels like there must be an easy way to do this, but at least
it works.

## read in the data from the /data/ folder ##

```{r}
data <- read_csv("data/d1.csv")
head(data)
```

ok, so this works nicely. 



## test out some different scenarios ##

e.g., download and create a new folder.
This is useful for git projects because empty folders do not exist.

let's see

```{r}
dir.create("data/new_folder/")
osf_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("jc82t") %>% ## this is just one project picked at random
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "prior") %>%
  osf_ls_files(pattern = "d1") %>%
  osf_download(path = "./data/new_folder/", conflicts = "overwrite")
```



## test out the tutorial data download ##

sim1

```{r}
dir.create("data/eha_tutorial")
dir.create("data/eha_tutorial/sim1")

osf_eha_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% ## this is just one project picked at random
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim1") %>%
  osf_ls_files(pattern = "sim1_data") %>%
  osf_download(path = "./data/eha_tutorial/sim1/")
```

sim2

```{r}
dir.create("data/eha_tutorial/sim2")

osf_eha_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% ## this is just one project picked at random
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim2") %>%
  osf_ls_files(pattern = "sim2_data") %>%
  osf_download(path = "./data/eha_tutorial/sim2/")
```

ok, that works.


## test out a loop to check if the folder and file exists ##

```{r}
output_dir <- here("data/eha_tutorial/test2/")

if (!dir.exists(here(output_dir))) {
  dir.create(here(output_dir))
}

file_name <- here("data/eha_tutorial/test2/sim2_data.csv")

if (!file.exists(here(file_name))) {
  osf_retrieve_node("3dbcs") %>% 
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim2") %>%
  osf_ls_files(pattern = "sim2_data") %>%
  osf_download(path = output_dir)
}
```

